Guilt, shame, and anti-war action in an authoritarian country at war

### 2023-04-30 manuscript.Rmd
Added header code to specify different font for Linux

---
title: "Guilt, shame, and anti-war action in an authoritarian country at war"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    keep_tex: yes
    toc: false
  html_document:
    df_print: paged
  bookdown::word_document2:
    toc: false
always_allow_html: true
header-includes:
  - \usepackage{indentfirst}
  - \usepackage{sectsty}
  - \allsectionsfont{\centering}
  - \usepackage{fontspec}
  - \usepackage{polyglossia}
  - \setdefaultlanguage{english}
  - \setotherlanguages{russian}
  - \setmainfont{Times New Roman}
  - \newfontfamily{\cyrillicfonttt}{Times New Roman} 
  - \usepackage{float} 
  - \usepackage{float} \floatplacement{figure}{H} 
  - \newcommand{\beginsupplement}{\setcounter{table}{0}    
  - \renewcommand{\thetable}{S\arabic{table}} 
  - \setcounter{figure}{0} 
  - \renewcommand{\thefigure}{S\arabic{figure}}}  
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
indent: true
bibliography: references.bib
csl: elife.csl
---

@@

packagelist <- c('readr','psych','GPArotation','lavaan','pscl','ggplot2','sjPlot', 'car','dplyr','MASS','writexl','readxl','kableExtra','rstatix')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

colnames(table1_numbers) <- c("$\\beta$", "$b$", "$SE$", "$p$", "$\\beta$", "$b$", "$SE$", "$p$", "$\\beta$", "$b$", "$SE$", "$p$")

knitr::kable(table1_numbers, caption='Predicting group-based guilt and shame from political beliefs',align='rrrrrrrrrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>% 
  kableExtra::add_header_above(c("", "Moral Shame" = 4, "Image Shame" = 4, "Guilt" = 4)) %>%
  row_spec(6,hline_after=T)

@@

knitr::kable(table2_numbers, caption='Predicting anti-war action from group-based guilt and shame', align='rrrrrrrrrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>% 
  kableExtra::add_header_above(c("", "Past Behaviour" = 4, "Behavioural Intention" = 4, "Action Probability" = 4)) %>%
  row_spec(4,hline_after=T)

@@

knitr::kable(table3_numbers, caption='Predicting future behavior from emotions and attitudes
', align='rrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position")

>>>>

---
title: "Guilt, shame, and anti-war action in an authoritarian country at war"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    keep_tex: yes
    toc: no
  word_document:
    toc: no
  bookdown::word_document2:
    toc: no
  html_document:
    df_print: paged
always_allow_html: yes
test: "`r OS <- Sys.info()['sysname']`
`r if (OS=='Linux'){fontname <- 'Nimbus Roman'}`
`r if (OS=='Darwin'){fontname <- 'Times New Roman'}`"
header-includes:
- \usepackage{indentfirst}
- \usepackage{sectsty}
- \allsectionsfont{\centering}
- \usepackage{fontspec}
- \usepackage{polyglossia}
- \setdefaultlanguage{english}
- \setotherlanguages{russian}
- \setmainfont{`r fontname`}
- \newfontfamily{\cyrillicfonttt}{`r fontname`}
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{S\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{S\arabic{figure}}}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
indent: yes
bibliography: references.bib
csl: elife.csl
---

@@

packagelist <- c('readr','psych','GPArotation','lavaan','pscl','ggplot2','sjPlot', 'car','dplyr','MASS','writexl','readxl','kableExtra','rstatix','tinytex')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

# download latex if not already present
if (!tinytex::is_tinytex()){tinytex::install_tinytex()}

@@

colnames(table1_numbers) <- c("$\\beta$", "b", "SE", "p", "$\\beta$", "b", "SE", "p", "$\\beta$", "b", "SE", "p")

knitr::kable(table1_numbers, caption='Predicting group-based guilt and shame from political beliefs',align='rrrrrrrrrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>% 
  kableExtra::add_header_above(c("", "Moral Shame" = 4, "Image Shame" = 4, "Guilt" = 4)) %>%
  row_spec(0,italic=T) %>%
  row_spec(6,hline_after=T)

@@

knitr::kable(table2_numbers, caption='Predicting anti-war action from group-based guilt and shame', align='rrrrrrrrrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>% 
  kableExtra::add_header_above(c("", "Past Behaviour" = 4, "Behavioural Intention" = 4, "Action Probability" = 4)) %>%
  row_spec(0,italic=T) %>%
  row_spec(4,hline_after=T)

@@

knitr::kable(table3_numbers, caption='Predicting future behavior from emotions and attitudes
', align='rrrrr', booktabs = TRUE, escape = FALSE) %>% 
  row_spec(0,italic=T) %>%
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position")

### 2023-04-30 manuscript.tex
Added header code to specify different font for Linux

\setmainfont{Times New Roman}
\newfontfamily{\cyrillicfonttt}{Times New Roman}

@@

\caption{\label{tab:Table1}Predicting group-based guilt and shame from political beliefs}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Moral Shame} & \multicolumn{4}{c}{Image Shame} & \multicolumn{4}{c}{Guilt} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
  & $\beta$ & $b$ & $SE$ & $p$ & $\beta$ & $b$ & $SE$ & $p$ & $\beta$ & $b$ & $SE$ & $p$\\
\midrule
Intercept & 0 & -2.89 & 0.32 & <.001 & 0 & -2.85 & 0.34 & <.001 & 0 & -2.93 & 0.34 & <.001\\
Democratic Values & 0.41 & 0.64 & 0.05 & <.001 & 0.4 & 0.64 & 0.05 & <.001 & 0.41 & 0.65 & 0.05 & <.001\\
Political Cynicism (politicians) & 0.18 & 0.2 & 0.05 & <.001 & 0.16 & 0.18 & 0.05 & <.001 & 0.09 & 0.1 & 0.05 & .039\\
Political Cynicism (politics) & -0.05 & -0.05 & 0.04 & .189 & -0.03 & -0.03 & 0.04 & .458 & -0.03 & -0.03 & 0.04 & .455\\
Political Alienation & -0.05 & -0.06 & 0.04 & .122 & -0.03 & -0.04 & 0.04 & .380 & 0.01 & 0.02 & 0.04 & .663\\
\addlinespace
Political Responsibility & 0.04 & 0.05 & 0.04 & .190 & 0.03 & 0.04 & 0.04 & .347 & 0.07 & 0.1 & 0.04 & .022\\
\midrule
R$^{2}$ &  & .260 &  &  &  & .234 &  &  &  & .221 &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:Table2}Predicting anti-war action from group-based guilt and shame}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Past Behaviour} & \multicolumn{4}{c}{Behavioural Intention} & \multicolumn{4}{c}{Action Probability} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
  & $\beta$ & b & SE & p & $\beta$ & b & SE & p & $\beta$ & b & SE & p\\
\midrule
Intercept & 0 & 0.1 & 0.04 & .009 & 0 & 1.09 & 0.03 & <.001 & 0 & 1.21 & 0.07 & <.001\\
Guilt & 0.02 & 0.01 & 0.04 & .756 & 0 & 0 & 0.03 & .942 & 0.05 & 0.06 & 0.06 & .326\\
Image Shame & -0.07 & -0.05 & 0.05 & .393 & 0.1 & 0.06 & 0.04 & .154 & -0.02 & -0.02 & 0.1 & .826\\
Moral Shame & 0.48 & 0.31 & 0.06 & <.001 & 0.56 & 0.33 & 0.05 & <.001 & 0.59 & 0.77 & 0.11 & <.001\\
\midrule
R$^{2}$ &  & .181 &  &  &  & .425 &  &  &  & .376 &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:Table3}Predicting future behavior from emotions and attitudes
}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
  & $\beta$ & b & SE & t-value & p\\
\midrule
Intercept & 0 & -0.1 & 0.12 & -0.82 & .410\\
Emotions: Positive & -0.032 & -0.03 & 0.03 & -0.96 & .337\\
Emotions: Negative Dominant & 0.237 & 0.19 & 0.03 & 6.4 & <.001\\
Emotions: Negative Submissive & -0.076 & -0.07 & 0.03 & -2.43 & .015\\
Attitudes towards the war & -0.152 & -0.12 & 0.03 & -3.77 & <.001\\
\addlinespace
Group-based moral shame & 0.36 & 0.22 & 0.05 & 4.63 & <.001\\
Group-based image shame & 0.002 & 0 & 0.04 & 0.03 & .977\\
Group-based guilt & 0.033 & 0.02 & 0.03 & 0.76 & .450\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:TableS2}Zero-inflated negative binomial regression predicting group-based guilt and shame from political beliefs.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrr}
\toprule
\multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Moral Shame}} & \multicolumn{3}{c}{\textbf{Image Shame}} & \multicolumn{3}{c}{\textbf{Guilt}} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
\em{ } & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p}\\
\midrule
\em{\textbf{Count model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & -0.76 & 0.31 & .014 & -0.44 & 0.29 & .129 & -0.85 & 0.28 & .002\\
Democratic values & 0.23 & 0.05 & <.001 & 0.17 & 0.05 & <.001 & 0.25 & 0.05 & <.001\\
Political cynicism (politicians) & 0.12 & 0.05 & .006 & 0.12 & 0.04 & .005 & 0.07 & 0.04 & .065\\
Political cynicism (politics) & -0.04 & 0.03 & .172 & -0.03 & 0.03 & .253 & -0.02 & 0.03 & .548\\
\addlinespace
Political alienation & -0.03 & 0.03 & .255 & 0 & 0.03 & .971 & 0 & 0.03 & .992\\
Political responsibility & 0.01 & 0.03 & .691 & 0 & 0.03 & .948 & 0.03 & 0.03 & .308\\
\midrule
\em{\textbf{Zero-inflation model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 5.03 & 0.63 & <.001 & 5.15 & 0.62 & <.001 & 4.17 & 0.6 & <.001\\
Democratic values & -0.74 & 0.1 & <.001 & -0.77 & 0.1 & <.001 & -0.67 & 0.09 & <.001\\
\addlinespace
Political cynicism (politicians) & -0.05 & 0.09 & .529 & -0.06 & 0.08 & .493 & 0.05 & 0.08 & .569\\
Political cynicism (politics) & -0.11 & 0.07 & .115 & -0.11 & 0.07 & .123 & -0.07 & 0.07 & .315\\
Political alienation & 0.02 & 0.07 & .730 & 0.04 & 0.07 & .579 & -0.06 & 0.07 & .369\\
Political responsibility & -0.05 & 0.07 & .528 & -0.05 & 0.07 & .492 & -0.07 & 0.07 & .295\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\setmainfont{Nimbus Roman}
\newfontfamily{\cyrillicfonttt}{Nimbus Roman}

@@

\caption{\label{tab:Table1}Predicting group-based guilt and shame from political beliefs}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Moral Shame} & \multicolumn{4}{c}{Image Shame} & \multicolumn{4}{c}{Guilt} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
\em{ } & \em{$\beta$} & \em{b} & \em{SE} & \em{p} & \em{$\beta$} & \em{b} & \em{SE} & \em{p} & \em{$\beta$} & \em{b} & \em{SE} & \em{p}\\
\midrule
Intercept & 0 & -2.89 & 0.32 & <.001 & 0 & -2.85 & 0.34 & <.001 & 0 & -2.93 & 0.34 & <.001\\
Democratic Values & 0.41 & 0.64 & 0.05 & <.001 & 0.4 & 0.64 & 0.05 & <.001 & 0.41 & 0.65 & 0.05 & <.001\\
Political Cynicism (politicians) & 0.18 & 0.2 & 0.05 & <.001 & 0.16 & 0.18 & 0.05 & <.001 & 0.09 & 0.1 & 0.05 & .039\\
Political Cynicism (politics) & -0.05 & -0.05 & 0.04 & .189 & -0.03 & -0.03 & 0.04 & .458 & -0.03 & -0.03 & 0.04 & .455\\
Political Alienation & -0.05 & -0.06 & 0.04 & .122 & -0.03 & -0.04 & 0.04 & .380 & 0.01 & 0.02 & 0.04 & .663\\
\addlinespace
Political Responsibility & 0.04 & 0.05 & 0.04 & .190 & 0.03 & 0.04 & 0.04 & .347 & 0.07 & 0.1 & 0.04 & .022\\
\midrule
R$^{2}$ &  & .260 &  &  &  & .234 &  &  &  & .221 &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:Table2}Predicting anti-war action from group-based guilt and shame}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Past Behaviour} & \multicolumn{4}{c}{Behavioural Intention} & \multicolumn{4}{c}{Action Probability} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
\em{ } & \em{$\beta$} & \em{b} & \em{SE} & \em{p} & \em{$\beta$} & \em{b} & \em{SE} & \em{p} & \em{$\beta$} & \em{b} & \em{SE} & \em{p}\\
\midrule
Intercept & 0 & 0.1 & 0.04 & .009 & 0 & 1.09 & 0.03 & <.001 & 0 & 1.21 & 0.07 & <.001\\
Guilt & 0.02 & 0.01 & 0.04 & .756 & 0 & 0 & 0.03 & .942 & 0.05 & 0.06 & 0.06 & .326\\
Image Shame & -0.07 & -0.05 & 0.05 & .393 & 0.1 & 0.06 & 0.04 & .154 & -0.02 & -0.02 & 0.1 & .826\\
Moral Shame & 0.48 & 0.31 & 0.06 & <.001 & 0.56 & 0.33 & 0.05 & <.001 & 0.59 & 0.77 & 0.11 & <.001\\
\midrule
R$^{2}$ &  & .181 &  &  &  & .425 &  &  &  & .376 &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:Table3}Predicting future behavior from emotions and attitudes
}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
\em{ } & \em{$\beta$} & \em{b} & \em{SE} & \em{t-value} & \em{p}\\
\midrule
Intercept & 0 & -0.1 & 0.12 & -0.82 & .410\\
Emotions: Positive & -0.032 & -0.03 & 0.03 & -0.96 & .337\\
Emotions: Negative Dominant & 0.237 & 0.19 & 0.03 & 6.4 & <.001\\
Emotions: Negative Submissive & -0.076 & -0.07 & 0.03 & -2.43 & .015\\
Attitudes towards the war & -0.152 & -0.12 & 0.03 & -3.77 & <.001\\
\addlinespace
Group-based moral shame & 0.36 & 0.22 & 0.05 & 4.63 & <.001\\
Group-based image shame & 0.002 & 0 & 0.04 & 0.03 & .977\\
Group-based guilt & 0.033 & 0.02 & 0.03 & 0.76 & .450\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:TableS2}Zero-inflated negative binomial regression predicting group-based guilt and shame from political beliefs.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrrrrrr}
\toprule
\multicolumn{1}{c}{\textbf{}} & \multicolumn{3}{c}{\textbf{Moral Shame}} & \multicolumn{3}{c}{\textbf{Image Shame}} & \multicolumn{3}{c}{\textbf{Guilt}} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
\em{ } & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p} & \em{b} & \em{SE} & \em{p}\\
\midrule
\em{\textbf{Count model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & -0.76 & 0.31 & .014 & -0.44 & 0.29 & .129 & -0.85 & 0.28 & .002\\
Democratic values & 0.23 & 0.05 & <.001 & 0.17 & 0.05 & <.001 & 0.25 & 0.05 & <.001\\
Political cynicism (politicians) & 0.12 & 0.05 & .006 & 0.12 & 0.04 & .005 & 0.07 & 0.04 & .065\\
Political cynicism (politics) & -0.04 & 0.03 & .172 & -0.03 & 0.03 & .253 & -0.02 & 0.03 & .549\\
\addlinespace
Political alienation & -0.03 & 0.03 & .255 & 0 & 0.03 & .971 & 0 & 0.03 & .993\\
Political responsibility & 0.01 & 0.03 & .691 & 0 & 0.03 & .948 & 0.03 & 0.03 & .308\\
\midrule
\em{\textbf{Zero-inflation model}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
\midrule
Intercept & 5.03 & 0.63 & <.001 & 5.15 & 0.62 & <.001 & 4.17 & 0.6 & <.001\\
Democratic values & -0.74 & 0.1 & <.001 & -0.77 & 0.1 & <.001 & -0.67 & 0.09 & <.001\\
\addlinespace
Political cynicism (politicians) & -0.05 & 0.09 & .529 & -0.06 & 0.08 & .493 & 0.05 & 0.08 & .569\\
Political cynicism (politics) & -0.11 & 0.07 & .115 & -0.11 & 0.07 & .123 & -0.07 & 0.07 & .315\\
Political alienation & 0.02 & 0.07 & .730 & 0.04 & 0.07 & .579 & -0.06 & 0.07 & .369\\
Political responsibility & -0.05 & 0.07 & .528 & -0.05 & 0.07 & .492 & -0.07 & 0.07 & .295\\
\bottomrule
\end{tabular}
\end{table}
